---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggstates

A package to map US state polygons easily from flat file. 

Note on name: ggusa felt too silly and ggunitedstatesamerica felt too long. There are other countries w/ 'states' in their name.

R's convenience datasets uses 'state' to refer to US states.

```{r, eval = F}
state.abb
state.area
state.center
state.division
state.name
state.region
state.x77
```

<!-- badges: start -->
<!-- badges: end -->


## Installation

You can install the development version of ggstates from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggstates")
```

## without ggstates

```{r}
library(sf)
library(tidyverse)

states_attributes <- state.x77 %>% 
  data.frame() %>% 
  rownames_to_column(var = "state")


# https://www.census.gov/geographies/mapping-files/time-series/geo/carto-boundary-file.html
states_geometries <- read_sf("data-raw/cb_2018_us_state_20m/cb_2018_us_state_20m.shp") %>%   
  filter(NAME != "Puerto Rico",
         NAME != "District of Colombia") %>% 
  select(STUSPS, NAME, geometry)


states_attributes %>% 
  left_join(states_geometries, by = c("state" = "NAME")) %>% 
ggplot() + 
  aes(geometry = geometry, state = state.name) +
  geom_sf() + 
  coord_sf() + 
  aes(fill = Income)
```

# With ggstates
 
```{r example}
library(ggplot2)
library(ggstates)

state_attributes |> head()

library(ggplot2)
ggplot(state_attributes) +
aes(state = state_name) +
geom_state()

ggplot(state_attributes) +
aes(state = state_name) +
geom_state(drop_state = c("Hawaii", "Alaska"))

ggplot(state_attributes) +
aes(state = state_name) +
geom_state(drop_state = c("Hawaii", "Alaska")) +
aes(fill = Frost)

last_plot() + 
  aes(fill = Population)

last_plot() + 
  aes(fill = Area)

ggplot(state_attributes) +
  aes(state = state_name) +
  geom_state(keep_state = c("New York", "Virginia", 
                            "Maryland", "West Virginia",
                            "Pennsylvania",
                            "New Jersey", "Delaware")) + 
  aes(fill = state_name)

ggplot(state_attributes) +
  aes(state = state_name) +
  geom_state(keep_state = c("CA", "WA", 
                            "OR", "NV")) + 
  aes(fill = state_name)

# rot = function(a) matrix(c(cos(a), sin(a), -sin(a), cos(a)), 2, 2)
# nc = st_read(system.file("shape/nc.shp", package="sf"), quiet = TRUE)
# ncg = st_geometry(nc)
# plot(ncg, border = 'grey')
# cntrd = st_centroid(ncg)
# ncg2 = (ncg - cntrd) * rot(pi/2) * .75 + cntrd
# plot(ncg2, add = TRUE)
# plot(cntrd, col = 'red', add = TRUE, cex = .5)
# 
# ggstates::state_reference_full %>% 
#   st_geometry() %>% 
#   mutate(geometry = ifelse(state_name == "Alaska", geometry + 100, geometry)) %>% 
#   sf::as_()
#   ggplot() + 
#   geom_sf(aes(geometry = geometry))

```
